A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-01 papers/gabb17/gabb17-pollard.tex
Updated scalability figure generation and pdfs.
Added .gitignore to ignore extra LaTeX files.

Slightly updated the .tex, still having issues with pgfplotstable.

\documentclass[conference]{IEEEtran}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{pgfplotstable}
\pgfplotsset{compat=1.12}
\usepackage{booktabs}

@@

\begin{table}
%	\begin{tabular}{l|r|r|}
%	 & PowerGraph & OpenG \\ \hline
%	BFS & 81.8 & 341 \\ \hline
%	SSSP & 1.64 & 15.0 \\ \hline
%	LCC & 54.6 & 142 \\ \hline
%	\end{tabular}
		\centering
		\pgfplotstabletypeset[
			col sep=comma,
			string type, % Makes the .style={string type} redundant
			columns={[index]0,GraphBIG,PowerGraph},
			every head row/.style={after row=\midrule},
			columns/0/.style={string type, column type={l|}, column name={}},
			columns/openg/.style={string type, column type={r}},
			columns/powergraph/.style={string type, column type={r}}
		]{../report/runtime.csv}
	\caption{Performance results are in milliseconds. LCC is local clustering coefficient, PR is PageRank, CDLP is community detection using label propagation, and WCC is weakly connected components}
	\label{tab:graphalytics}
\end{table}

The following figures are not useful. They were are merely placeholders while further experiments are being run using the correct number of threads and roots. These issues are especially noticeable in GraphBIG.
\begin{table}[!htb]
	\centering
	\begin{tabular}{l|c|c|c}
		System & Load Graph & \begin{tabular}[x]{@{}c@{}}Construct Data \\ Structure\end{tabular} & Run BFS \\ \hline
		Graph500 & 0.3474 & 0.3971 & 0.003380 \\
		GraphBIG & 37.22  & N/A    & 0.1528 \\
		GraphMat & 0.1511 & 1.101  & 0.1031 \\
		GAP      & 2.351  & 0.1935 & 0.001393 \\
	\end{tabular}
	\caption{The above table shows times for $2^{20}$ verties and the times are in seconds. The Graph500 generates the graph instead of loading it into a file. GraphBIG builds the graph and reads in the file simultaneously. These results were averaged across 32 roots.}
	\label{tab:fileload}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=0.8\columnwidth]{graphics/bfs_time.pdf}
	\vspace{-18pt}
	\caption{The $y$-axis is logarithmic. [TODO: Replace this with the data with non-zero degree vertices]}
	\label{fig:bfs-time}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\columnwidth]{graphics/pr_iters.pdf}
	\vspace{-18pt}
	\caption{The $y$-axis \emph{not} logarithmic. GraphMat iterations are measured differently because of the ``think like a vertex'' paradigm and runs unitl none of the vertices' ranks change.}
	\label{fig:pr-iters}
\end{figure}
[Note that for figure Fig.\ref{fig:pr-iters}, mention time per iteration]

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\columnwidth]{graphics/bfs_ss.pdf}
	\vspace{-18pt}
	\caption{The $y$-axis \emph{not} logarithmic. GraphMat iterations are measured differently because of the ``think like a vertex'' paradigm and runs unitl none of the vertices' ranks change. [There is only one data point]}
	\label{fig:bfs-ss}
\end{figure}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{pgfplotstable}
\usepackage{array} % Required for pgfplotstable dec sep align
\pgfplotsset{compat=1.12}
\usepackage{booktabs}

@@

\begin{table}
%	\begin{tabular}{l|r|r|}
%	 & PowerGraph & OpenG \\ \hline
%	BFS & 81.8 & 341 \\ \hline
%	SSSP & 1.64 & 15.0 \\ \hline
%	LCC & 54.6 & 142 \\ \hline
%	\end{tabular}
		\centering
		\pgfplotstabletypeset[
			col sep=comma,
			columns={[index]0,GraphBIG,PowerGraph},
			every head row/.style={after row=\midrule},
			columns/0/.style={string type, column type={l|}, column name={}},
			columns/openg/.style={dec sep align},
			columns/powergraph/.style={dec sep align}
		]{../report/runtime.csv}
	\caption{Performance results are in milliseconds. LCC is local clustering coefficient, PR is PageRank, CDLP is community detection using label propagation, and WCC is weakly connected components}
	\label{tab:graphalytics}
\end{table}

The following figures are not useful. They were are merely placeholders while further experiments are being run using the correct number of threads and roots. These issues are especially noticeable in GraphBIG.
\begin{table}[!htb]
	\centering
	\begin{tabular}{l|c|c|c}
		System & Load Graph & \begin{tabular}[x]{@{}c@{}}Construct Data \\ Structure\end{tabular} & Run BFS \\ \hline
		Graph500 & 0.3474 & 0.3971 & 0.003380 \\
		GAP      & 2.351  & 0.1935 & 0.001393 \\
		GraphMat & 0.1511 & 1.101  & 0.1031 \\
		GraphBIG & 37.22  & N/A    & 0.1528 \\
	\end{tabular}
	\caption{The above table shows times for $2^{20}$ verties and the times are in seconds. The Graph500 generates the graph instead of loading it into a file. GraphBIG builds the graph and reads in the file simultaneously. These results were averaged across 32 roots.}
	\label{tab:fileload}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=0.8\columnwidth]{graphics/bfs_time.pdf}
	\vspace{-18pt}
	\caption{The $y$-axis is logarithmic.}
	\label{fig:bfs-time}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\columnwidth]{graphics/pr_iters.pdf}
	\vspace{-18pt}
	\caption{The $y$-axis \emph{not} logarithmic. GraphMat iterations are measured differently because of the ``think like a vertex'' paradigm and runs until none of the vertices' ranks change.}
	\label{fig:pr-iters}
\end{figure}
[Note that for figure Fig.\ref{fig:pr-iters}, mention time per iteration]

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\columnwidth]{graphics/bfs_ss.pdf}
	\vspace{-18pt}
	\caption{Strong Scaling for $2^{20}$ vertices and an average of 16 edges per vertex.}
	\label{fig:bfs-ss}
\end{figure}

\begin{figure}
	\centering
	% trim left bottom right top
	\includegraphics[width=\columnwidth, trim=0 18pt 18pt 0, clip]{graphics/bfs_speedup.pdf}
	\caption{Speedup.}
	\label{fig:bfs-speedup}
\end{figure}
